%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Latin Teacher} % Job title
    {Parkway School District} % Organization
    {St. Louis, USA} % Location
    {August 2016 - June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Increased student engagement and retention by introducing spoken Latin to classes.}
        \item {Introduced research-based language teaching practices (focused on Comprehensible Input, plus Teaching Proficiency through Reading and Storytelling).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Latin Teacher} % Job title
    {Collegiate School of Medicine and Biosciences} % Organization
    {St. Louis, USA} % Location
    {August 2015 - June 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Began learning to speak Latin with students; studied research supporting CI and TPRS in language teaching.}        
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Instructor} % Job title
    {University of Oxford, Dept. of Continuing Education} % Organization
    {online} % Location
    {September 2014 - June 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught online courses in Philosophy of Mind and Philosophy of Science to a wide range of international students --- from high school student to retired professors in the sciences, and one member of the Japanese Parliament.}
        \item {Successfully managed online discussions, often needing to gently correct mistaken understandings of the material, sometimes also calming heated arguments.}
        \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Postdoctoral Researcher in Ancient Greek Philosophy} % Job title
    {University of Oxford} % Organization
    {Oxford, England, UK} % Location
    {October 2011 - September 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned, carried out, and published four original research articles on ancient theories of reality:  two of these in first-tier journals, other two in second-rank journals.}
        \item {Worked with team of researchers to support and promote extensive activities of our group:  frequent academic conferences, visiting lectures, regular seminars, and aggressive publishing program.}
        \item {Co-organized and helped run five international conferences.}
        \item {Co-edited a volume of new research relating to team's program; book was published on schedule with favorable reviews by the top publisher of academic philosophy books in the world (Cambridge University Press) with invitation from editor to propose new projects.}
        \item {Delivered talks on my research at international conferences and by invitation at several European universities.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Philosophy Professor} % Job title
    {Houston Community College} % Organization
    {Houston, Texas, USA} % Location
    {August 2010 - May 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught introductory courses in philosophy, ethics, and logic.}
	    \end{cvitems}
      }

%---------------------------------------------------------
  \cventry
  {} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Further entries omitted for brevity; full details available on request.}
      \end{cvitems}
    }


%---------------------------------------------------------
% \cventry
%   {Freelance Penetration Tester} % Job title
%    {SAMSUNG Electronics} % Organization
%    {S.Korea} % Location
%   {Sep. 2013, Mar. 2011 - Oct. 2011} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Conducted penetration testing on SAMSUNG KNOX, which is solution for enterprise mobile security.}
%        \item {Conducted penetration testing on SAMSUNG Smart TV.}
%      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
%    }

%---------------------------------------------------------
\end{cventries}
